Effect of Nanovoid on Fracture Process of Two-Phase $\alpha$($\rm TiAl$)+$\gamma$($\rm Ti_3Al$) Alloy

### 2018-08-04 draft/scpt.tex
add virial stress

\paragraph{stress calculation}

@@

%\begin{figure}
%	\centering
%	\includegraphics[width=0.5\linewidth]{pict/model_labeled}
%	\caption{Representative nanocrystalline bulk mode}
%	\centering
%	\label{fig:pf_model}
%\end{figure}
\subsection{Identification of Defects}
\paragraph{}
 \begin{table}[h]
 	\centering
 	\caption{Table caption}
 	\begin{tabular}{l l l}
 		\hline
 		\textbf{Treatments} & \textbf{Response 1} & \textbf{Response 2}\\
 		\hline
 		Treatment 1 & 0.0003262 & 0.562 \\
 		Treatment 2 & 0.0015681 & 0.910 \\
 		Treatment 3 & 0.0009271 & 0.296 \\
 		\hline
 	\end{tabular}

 \end{table}

$$E=\sum_{i}^n a_i=0$$

where

parameters can be given as Table \ref{Tab:par}:

\section{Results and Discussion}

>>>>

\paragraph{stress calculation}
The atomic stress is calculated using the virial definition :
$$\sigma_t(i)=-$$
$$\sigma_t(i)= $$
where $\f_\alpha$ is the interatomic force between atom i and j in the direction $\alpha$, $\gamma_\beta$ is the distance in direction

@@

%\begin{figure}
%	\centering
%	\includegraphics[width=0.5\linewidth]{pict/model_labeled}
%	\caption{Representative nanocrystalline bulk mode}
%	\centering
%	\label{fig:pf_model}
%\end{figure}
\subsection{Identification of Defects}
%\paragraph{}
% \begin{table}[h]
% 	\centering
% 	\caption{Table caption}
% 	\begin{tabular}{l l l}
% 		\hline
% 		\textbf{Treatments} & \textbf{Response 1} & \textbf{Response 2}\\
% 		\hline
% 		Treatment 1 & 0.0003262 & 0.562 \\
% 		Treatment 2 & 0.0015681 & 0.910 \\
% 		Treatment 3 & 0.0009271 & 0.296 \\
% 		\hline
% 	\end{tabular}
% 	
% \end{table}
%
%
%$$E=\sum_{i}^n a_i=0$$
%
%where
%
%
%parameters can be given as Table \ref{Tab:par}:
%
%
%
\section{Results and Discussion}
